% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{url}
\usepackage{hanging}
\usepackage{parskip}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}

% Set your name here
\def\name{Tin Nguyen}

% Replace this with a link to your CV if you like, or set it empty
% (as in \def\footerlink{}) to remove the link in the footer:

% The following metadata will show up in the PDF properties
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {economics, statistics, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Customize page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Other possible font commands include:
% \ttfamily for teletype,
% \sffamily for sans serif,
% \bfseries for bold,
% \scshape for small caps,
% \normalsize, \large, \Large, \LARGE sizes.

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\begin{document}

% Place name at left
{\huge \name}

% Alternatively, print name centered and bold:
%\centerline{\huge \bf \name}

\vspace{0.25in}

\begin{minipage}{0.45\linewidth}
  73/2/1 Ni Su Huynh Lien\\
  Ward 10, Tan Binh district\\
 Ho Chi Minh city, Vietnam\\
 
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Email: & \href{mailto:nttin@apcs.vn}{\tt nttin@apcs.vn} \\
    Phone: & {\tt 0918644143} \\
    Website: & \href{http://tintrongnguyen.me}{\tt tintrongnguyen.me} \\
    Github: & \href{https://github.com/v36372}{\tt @v36372} \\
  \end{tabular}
\end{minipage}

\section*{Education}

\begin{itemize}
  \item Bachelor of Computer Science, Ho Chi Minh University of Science, 2012 - 2016. 
\end{itemize}

\section*{Employment history}
\begin{itemize}
\item {\bf JOY Entertainment | 03/2015 - 09/2015}
\\
\\
JOY was a medium-size game studio based in Saigon, Vietnam. I joined this company to try out working in the game industry. Making game was something I interested in back in university days.
\\
\\
I was assigned to a C++ team to build and mantain a shooter game called Captain Strike.
\\
% \subitem Research Assistant for Stephen Ansolabehere at Harvard University (2012 -- current)\\


\leftskip 0in
\item {\bf Shelfout.com | 09/2015 - 02/2016}
\\
\\
Shelfout is a small start-up founded by friends of mine. We had a vision to build a book sharing platform. The project was a failure but we'd learnt so much since then.
\\
\\
We used Django web framework.
\\
You can visit our website here : 
\href{http://shelfout.com}{http://shelfout.com}
% \subitem Research Assistant for Stephen Ansolabehere at Harvard University (2012 -- current)\\


\leftskip 0in
\item {\bf Floating Cube Studios | 06/2016 - 06/2017}
\\
\\
FCS build point of sale products for small to middle size clients in Singapore. Our product isn't that good compare to other competitors. What brings us a lot of clients is a good internet domain name.
\\
\\
We fork Odoo and add customizations according to client's requests.
\\
\\
\end{itemize}
\section*{Projects}
\begin{itemize}
\item{\bf Sunseeker}
\\
\\
The project is a react front-end implementation for Dotastats, which I also contributed into.

We crawled e-sports matches and statistics from various betting websites. Then we organize, display them in a sane way. The purpose of this project is to win bets ofcourse.

The site can be found at \href{https://github.com/v36372/sunseeker}{\tt Sunseeker}
\\
\\
\item{\bf Golang web application boilerate}
\\
\\
I started this project to make my life and golang developers fellow easier. Where using web frameworks in Golang is a bad idea, it's quite confusing to organize and set up necessary parts. I started this project to make my life and golang developers fellow easier.

I looked at good examples of Golang web application and set up a base application with all the components in-place: middleware, router, handler, configuration, database, etc...

Still a work-in-progress

The project can be found at \href{https://github.com/v36372/base}{\tt Base}
\\
\\
\item{\bf Markstream}
\\
\\
This one is my university graduation thesis. The idea is to stream audio data with watermarks embedded.

In my case, to embed a watermark into an audio segment means altering the frequencies so that they contain my information.

To make the audio quality less degraded as possible, I need to apply a reasonable amount of modifications to the selected frequencies. There are some sensitive frequencies that are best to skip. Here I apply a dynamic scheme to determine how much should I change for a particular frequency.

The thesis is finished but there are still ideas to be improved on. I thought about recognizing audio parts where it's hard to embed and skip those, minimizing the error rate.

The project can be found at \href{https://github.com/v36372/markstream}{\tt Markstream}
\end{itemize}
\section*{Motivation}
After 1 year of doing software in small scope, I now want to do something bigger. I'd love to tackle techincal problems that the application faces when it grows large enough.
\\
\\
I'd love to work in something I don't have prior knowledge. I've been picking up new technical topics very often. I think this is one of my strong points.
\bigskip

% Footer
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
  \end{footnotesize}
\end{center}

\end{document}
