\chapter{Personal Development}
\section{Self-evaluation}
\subsection{My role and impact}
In the team, I act as a software developer that responsible for the front-end mobile development. I mainly focus on the technical side of the project.
\\
\\
As the project went on, I've put a lot of effort in the development of the application. It's because that my perfomance affects a lot on the project result where stable verison of the mobile application must be present. There many areas that would be malfunctioned or incomplete without me.
\\
\\
I am also responsible for programming and set up of the crawler that pulls data everyday to our mobile application. It's obvious that without the data stream, the app would have nothing to present to the user and become useless. Besides, setting a crawler requires serious work as well. Using of resources and exception handling must be taken care.
\\
\\
In the development of mobile application, I personally involve in alot of programming tasks that shape the current version of our app. There are many complex features that I invest a lot of hours in to make it plausible.
\begin{itemize}
\item{Infinite loading of feeds}
\item{Map navigation}
\item{Analytics}
\item{Capturing images}
\end{itemize}
\subsection{Personal and professional growth}
There are some positive changes that I have after finishing the project, both in technical and non-technical areas.
\\
\\
In the beginning of the project, there is a requirement that I have to be able to set up crawler for our application data. At the time I have no prior experience working with a crawler, therefore, I conduct a research into this field. After going online and study many crawling technologies, I decide to pick up Scrapy \cite{scrapy}, a crawler written in Python. I used Scrapy to set up our crawler for the application. After complete the project, I now familiar with the technology and would be confident with any requirement in crawling services in the future.
\\
\\
Although I am purely a technial engineer, I also realize that I've acquired a useful skill from the project that is non-technical. As a programmer, I focus only on my code of perfomance, but when working in team, there are many other things to keep in mind. One of them is to be commitment. The project is not only for me but also for my team. Without commitment, the engineer would't put his heart into his work and end up letting teammates down.
\\
\\
In the future, there are apparently a lot more things I have to learn. But through this project, I realized that the skillset I have is not enough to working in the industry. Therefore, I will put my focus on improving my expertise in engineering.
\section{Team evaluation}
In general, all member of my team did an excellent job finishing this project, which is huge in its own terms. There are some lags here and there in the duration of the project. Where we communicate the the client and advisor poorly. Especially at the middle of the project timeline, there is a distraction among team members. The team is disconnected and everyone end up doing their tasks and repor. Aware of the situation, we held more offline meetings and work together. This really boosts the team motivation and concentration. 
\\
\\
My experience working with the team is great. I communicate with the team frequently if there are any issue and willing to help other if they ran into problems.