\chapter{Team Evaluation}
\section{Nguyen Tran Phuong Nguyen}
Mrs. Nguyen is the team leader and project manager. She also took part in some designing phases such as application logo and UI polishing.
\\
\\
As a team leader, she took responsibility to contact and set up meetings with the client,Mr. Ho Ngoc Lam, and the advisor, Mr. Lam Quang Vu. The project required constant feedback from the client and report to the advisor, therefore Mrs. Nguyen's job could not be taken lightly. Generally, she had done a good job being a leader to keep the team together and an agent to transfer messages between the 3 parties in this projec: the team, the client, and advisor. 
\\
\\
As a project manager, being familiar with the SRUM software developement method, Mrs. Nguyen set up sprints and milestones for the team to look up on. Tasks were broken down into smaller owns and distributed evenly to every members based on the number of hours committed per week. She made sure that progress is frequently updated within less than a week. If there were any issue, she noted down and contact with Mr. Lam Ho for feedback.
\\
\\
Despite taking two roles at a time, Mrs. Nguyen exhibited an outstanding performance that contributed a lot to the team final achievement.
\section{Nguyen Quang Minh}
Mr. Minh is the teachnical lead of this project, he took care of the back-end development and proposed some ideas for the front-end solutions. Mainly, Mr. Minh focused on creating server side application, database and many other small services that amazingly worked together as a whole.
\\
\\
Throughout the project, Mr. Minh has shown an excellent display of performance, with his broad experience in technical background, he quickly point the development team to the right direction. It's very fortunate to have someone reliable with software development technologies, as it was prone to make the incorrect technical choices and waste time, while the project timeline is quite strict. At first, it was solitude that the Ionic framework would be used. On the back-end, Mr. Minh suggest Ruby-on-Rails would be the right way to go, whereas me and Mr. Tien prefer NodeJS. Mr. Minh then went on and discuss the good and bad points of each solutions very clearly, therefore, we decided to went for his propose. Later, in the development phase of the project, it appeared that Ruby-on-Rails did ease down the amount of work for this massive project, NodeJS would have created chaos that we couldn't control. There are many other situations where Mr. Minh stood out to propose a reasonable solution that help the team a lot.
\\
\\
In my general opinion, Mr. Minh is well-deserved an acknowledgement for his effort in this course.
\section{Tran Dinh Duy}
Mr. Duy took charge on the grapghic designing in general. Graphical designing requires a lot of effort to deliver a suitable solution for the application user interface. However, Mr. Duy utilize his experience in this field and complete his tasks well.
\\
\\
Our client, Mr. Lam Ho, has a slightly focus on the graphical interface and user experience. Luckily, Mr. Duy has been working in the industry for a long enough time, thanks to him we were able to adapt to those requirements. In the development process, Mr. Duy has frequently complete complex designing tasks that have a lot of strict guidelines. Although, graphical interface is widely varied from projects to projects, he willingly researched into the category of our mobile application.
\\
\\
I highly evaluate Mr. Duy professional abilities and his work ethic that demonstrate the effort he put in this project.
\section{Nguyen Nhat Tien}
Mr. Tien sided with me to develop the mobile application based on the Ionic framework. In this project, the mobile appication is our concentration, it's very important that a stable, working version is produced. Therefore, Mr. Tien and I put a lot of effort in the process, from the beginning to the end.
\\
\\
Mr. Tien has performed very well throughout the project. He completed tasks on time, report progress every time a feature was online or an issue came up. He is a decent engineer with strong ground basic skill in web development, which is a majority of this project.
\section{Duong Gia Tuan}
Mr. Tuan took the role as an application tester for the team. Report any bugs and errors to the development team on time. He also put effort in preparing reports and documents for the project.
\\
\\
Throughout 6 months of project timeline, Mr. Tuan has shown a constant enthusiasm for the project, although he lacks skill in bothprogramming and designing. He shown up in most of weekly meetings and put up a professional attitude to the client and the advisor.
\section{Nguyen Trong Tin}
I was responsible for the mobile application development and the programming, setting up of data crawler. My work and self-evaluation is examined closer at Chapter 4 - Personal Development.